{\boldmath Pseudoscalar top-Higgs coupling: Exploration of $\mathrm{CP}$-odd observables to resolve the sign ambiguity }

### 2016-03-08 Paper_ttbarH_Draft.tex

\begin{abstract}
\vspace*{4mm} We present a collection of $\mathrm{CP}$-odd observables
for the process $\ppprocess$ that are linearly dependent on the scalar
($\kp$) and pseudoscalar ($\kpt$) top-Higgs coupling and hence
sensitive to the corresponding relative sign. The proposed observables
are based on triple product (TP) structures that we extract
from the expression of the differential cross section in terms of the
spin vectors of the top and antitop quarks. In order to explore other
possibilities, we progressively modify these TPs, first
by combining them, and then by replacing the spin vectors by the
lepton momenta or the $t$ and $\tbar$ momenta by their visible parts.
Assuming an integrated luminosity that is consistent with that
  envisioned for the HL-LHC, we find that the most
promising observable can disentangle the hypotheses $\kp=1,\kpt=\pm 1$
by more than the $\sim 20\sigma$ statistical level ({\bf N: OK to keep ``disentangle" here or do we need to change to something like ``can disentangle the hypotheses with effective separations of order...?"}).  In
the case of observables that do not need the reconstruction of the $t$
and $\tbar$ momenta, the power of discrimination is up to the $\sim
16\sigma$ statistical level for the same number of events. We also show that the
capability of the most promising observables for separating the
$\mathrm{CP}$-mixed hypotheses preveals even when a number of events
plausible within the short term LHC is considered.

>>>>

\begin{abstract}
\vspace*{4mm} We present a collection of $\mathrm{CP}$-odd observables
for the process $\ppprocess$ that are linearly dependent on the scalar
($\kp$) and pseudoscalar ($\kpt$) top-Higgs coupling and hence
sensitive to the corresponding relative sign. The proposed observables
are based on triple product (TP) structures {\bf (N: correlations?)} that we extract
from the expression of the differential cross section in terms of the
spin vectors of the top and antitop quarks. In order to explore other
possibilities, we progressively modify these TPs, first
by combining them, and then by replacing the spin vectors by the
lepton momenta or the $t$ and $\tbar$ momenta by their visible parts.
Assuming an integrated luminosity that is consistent with that
  envisioned for the HL-LHC, we find that the most
promising observable can disentangle the hypotheses {\bf (N: scenarios?)} $\kp=1,\kpt=\pm 1$
by more than the $\sim 20\sigma$ statistical level {\bf (N: OK to keep ``disentangle" here or do we need to change to something like ``can disentangle the hypotheses with effective separations of order...?")}.  In
the case of observables that do not need the reconstruction of the $t$
and $\tbar$ momenta, the power of discrimination is up to the $\sim
16\sigma$ statistical level for the same number of events. We also show that the
capability of the most promising observables for separating the
$\mathrm{CP}$-mixed hypotheses preveals even when a number of events
plausible within the short term LHC is considered.
